|

### 2020-06-04 paper/Manuscript.Rmd
recomend knitr::read_chunk()
closes #75

In the R-implementation of WORCS, we recommend centering a research project
around one dynamically generated 'RMarkdown' document, which includes all 
analysis code. Longer scripts can be
stored in `.R` files, and called from the main document using the `source()`
function. When a reader or reviewer compiles this document, all code is run
automatically, thus verifying computational replicability. The 'RMarkdown' 
document can be automatically formatted in many styles, including
APA style [thanks to the R package `papaja`, @austPapajaPrepareReproducible2020],
a host of other scientific formats 
[see @allaireRticlesArticleFormats2020], and as plain 'Markdown'.

>>>>

In the R-implementation of WORCS, we recommend centering a research project
around one dynamically generated 'RMarkdown' document, which includes all 
analysis code. Longer scripts can be
stored in `.R` files, and included in the main document using the [`read_chunk()`
function](https://github.com/yihui/knitr-examples/blob/master/113-externalization.Rmd) from the `knitr` package, which comes together with the `rmarkdown` package. When a reader or reviewer compiles this document, all code is run
automatically, thus verifying computational replicability. The 'RMarkdown' 
document can be automatically formatted in many styles, including
APA style [thanks to the R package `papaja`, @austPapajaPrepareReproducible2020],
a host of other scientific formats 
[see @allaireRticlesArticleFormats2020], and as plain 'Markdown'.
